### 2018-12-14 README.Rmd
short sf example

```{r sf-output}
aw_interpolate(wards, tid = "WARD", source = race, sid = "GEOID",  
               weight = "sum", output = "sf", 
               extensive = c("TOTAL_E", "WHITE_E", "BLACK_E"))
```

>>>>

```{r sf-output}
aw_interpolate(wards, tid = "WARD", source = race, sid = "GEOID",  
               weight = "sum", output = "sf", extensive = "TOTAL_E")
```
